A decade of lost precision: Introducing a general framework for image feature matching without geometric constraints

### 2014-04-15 text/journal/paper.tex
Last updates to paper

In terms of computational complexity the algorithms can be implemented 
in $O(n\log n)$, if we assume that both the \emph{query} and the 
\emph{target} image has $n$ feature points. For a target image with $m$ 
features where $m$ is significantly different from $n$ the complexities 
are as noted in Table~\ref{table:running_times}. Note that 
implementations refer to the algorithms as specified in 
Table~\ref{table:distinctness}. In practice the constant factors 
involved in the actual matching of two images with approximately the 
same amount of feature points are usually small enough that all the 
algorithms run at a similar speed. To illustrate 
Table~\ref{table:running_times} contains the running times as measured 
while matching 15 3D objects under three different lighting conditions 
($42$ image pairs were matched in total). The running times are averaged 
over three separate runs of each algorithm implemented using the same 
data structures and libraries in Python.

@@

With the framework we introduced three simple methods that are all 
applicable in situations where \emph{Ratio-Match} is currently used.  
\emph{Self-Match} is on par with \emph{Ratio-Match} across all 
evaluations but can be applied when matching multiple overlapping 
images. \emph{Ratio-Match-Ext} and \emph{Mirror-Match} on the other hand 
can easily replace \emph{Ratio-Match} without any performance penalty 
and with an increase in precisionon but are both limited to matching 
image pairs like \emph{Ratio-Match}.

>>>>

In terms of computational complexity the algorithms can be implemented 
in $O(n\log n)$, if we assume that both the \emph{query} and the 
\emph{target} image has $n$ feature points. For a target image with $m$ 
features where $m$ is significantly different from $n$ the complexities 
are as noted in Table~\ref{table:running_times}. In practice the constant factors 
involved in the actual matching of two images with approximately the 
same amount of feature points are usually small enough that all the 
algorithms run at a similar speed. To illustrate 
Table~\ref{table:running_times} contains the running times as measured 
while matching 15 3D objects under three different lighting conditions 
($42$ image pairs were matched in total). The running times are averaged 
over three separate runs of each algorithm implemented using the same 
data structures and libraries in Python.

@@

With the framework we introduced three simple methods that are all 
applicable in situations where \emph{Ratio-Match} is currently used.  
\emph{Self-Match} is on par with \emph{Ratio-Match} across all 
evaluations but can be applied when matching multiple overlapping 
images. \emph{Ratio-Match-Ext} and \emph{Mirror-Match} on the other hand 
can easily replace \emph{Ratio-Match} without any performance penalty 
and with an increase in precision but are both limited to matching 
image pairs like \emph{Ratio-Match}.
